---
output: github_document
---

```{r, include=FALSE}
library(MOrepoTools)
```

# Converting xml files to plain text format

The instance files are in xml format but can be converted to a plain text file using an xslt
stylesheet. You need a stylesheet xml parser such as [xsltproc](http://xmlsoft.org/XSLT/xsltproc2.html).


## Convert assignment problems to Tuyttens raw format

The instances in [Tuyttens00](https://github.com/MCDMSociety/MOrepo-Tuyttens00) use the following 
format:

```
n 
c^{0}_{0,0}... c^{0}_{0,n-1}
c^{0}_{1,0}... c^{0}_{1,n-1}
...
c^{0}_{n-1,0}... c^{0}_{n-1,n-1}
c^{1}_{0,0}... c^{1}_{0,n-1}
c^{1}_{1,0}... c^{1}_{1,n-1}
...
c^{1}_{n-1,0}... c^{1}_{n-1,n-1}
```

where 

* $n$ = dimension/size
* $c^{k}_{r,c}$ = $k$'th cost of assigning row $r$ to column $c$.

The biAP instances can be converted to this format using stylesheet `convert_to_tuyttens.xsl`. From 
R (or commandline) run:

```{r}
system("xsltproc --output AP_instance_tuyttens.raw convert_to_tuyttens.xsl AP_instance.xml")
```

which generates file [AP_instance_tuyttens.raw](./AP_instance_tuyttens.raw) from the xml file 
[AP_instance.xml](./AP_instance.xml).


